Scheduling and Vectorization for MPC

### 2022-03-05 paper_SIMD.tex
Uncommented Ishaq's section.

\ana{Commenting out this section to have paper compile on Github. Will revert!}
\begin{comment}

@@

\ishaq{TODO: @Ana: I am still confused about what prevents a reviewer from saying, "you argue correctness of the schedule from unrolled MPC, you don't argue it for the pre-unrolled CFG that you use". Please comment.} \ana{The correctness proof answer this question. The unrolled schedule is the \emph{concretization} of MPC source. We define (1) the obvious $\gamma$, (2) we define partial order over MPC source codes (this is our abstract domain $A$), and (3) a partial order over unrolled schedules. Then we prove two theorems that $A \le A' \Rightarrow \gamma(A) \subseteq \gamma(A')$ and that the MPC source $\le$ Vectorized MPC source.}

\end{comment}

>>>>

\ana{Commenting out this section to have paper compile on Github. Will revert!}
%\begin{comment}

@@

%\ishaq{TODO: @Ana: I am still confused about what prevents a reviewer from saying, "you argue correctness of the schedule from unrolled MPC, you don't argue it for the pre-unrolled CFG that you use". Please comment.} \ana{The correctness proof answer this question. The unrolled schedule is the \emph{concretization} of MPC source. We define (1) the obvious $\gamma$, (2) we define partial order over MPC source codes (this is our abstract domain $A$), and (3) a partial order over unrolled schedules. Then we prove two theorems that $A \le A' \Rightarrow \gamma(A) \subseteq \gamma(A')$ and that the MPC source $\le$ Vectorized MPC source.}

%\end{comment}
